---
title: "Process data"
author: "Stefano Coretta"
date: "20/05/2019"
output: 
  html_document: 
    highlight: tango
    number_sections: yes
    theme: paper
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
# here package needed
knitr::opts_knit$set(root.dir = here::here())
library(tidyverse)
library(speakr) # https://github.com/stefanocoretta/speakr
```

# Tangle and weave

```{r tangle}
lmt("./data-raw/code/english.praat.md")
```

```{r wave}
system("pandoc -f gfm -o ./data-raw/code/english.pdf ./data-raw/code/english.praat.md -N --syntax-definition=/Users/stefano/.pandoc/pandoc-praat/praat.xml --highlight-style=/Users/stefano/.pandoc/flamenco.theme --metadata-file=./data-raw/code/english.yaml")
```

# Convert audio

The audio files are stereo, so we convert them to mono. The audio files are also downsampled to 2250 Hz.

```{r convert}
praat_run("./data-raw/code/convert.praat")
```

# Force-alignment

Run SPPAS on the files and correct the alignment.

# Detect burst onsets and create merged annotation TextGrids

This script finds the burst onsets of C1 and C2 and creates a merged TextGrid with all the relevant annotations.

```{r merge}
praat_run("./data-raw/code/make-textgrid.praat")
```

Now the merged annotation TextGrid (`[ID]-annotation.TextGrid`) can be corrected (`[ID]-annotation-corrected.TextGrid`).

# Get measurements

We can now extract all the relevant measurements from the corrected annotation TextGrids. The output is saved in `data-raw/datasets`.

```{r get-measures}
praat_run("./data-raw/code/get-measurements.praat")
```
